---
title: "Lab 8 - Linear Regression in R"
author: "Bridget Gibbons"
date: "11/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Load tidyverse, read in data

```{r}
library(tidyverse)

salmon <- read_csv("salmon_edited.csv")
```

##Explore data

```{r}
salmon_scatter <- ggplot(salmon, aes(x = year, y = salmon_fresh)) +
  geom_point()

salmon_scatter

#Overall, the data looks linear. Something seems to have happened around 2004 and 2013 that is non-linear
```

##Linear regression

```{r}
salmon_model <- lm(salmon_fresh ~ year, data = salmon)

salmon_model

```

Imports(tons) = -14982940 + 7550(Year)

Slope means the change in salmon imports over time in years.
Y intercept is the initial value for year 0. That's concerning because it is finding the intercept at year 0 instead of during the first year of the data set in the model (1990).

##Model diagnostics

```{r}
plot(salmon_model)

#Residuals appear normally distributed for the most part, with some data points that could be potential outliers.

par(mfrow = c(2,2))
plot(salmon_model)

```

##Model fit and significance

```{r}
summary(salmon_model)
```

Year does significantly predict salmon imports. R2 value means the fraction of the variance in y that is explained by x, or the fraction of the variation in salmon imports that is explained by year. 6% is not explained by year.

##Prepare a final graph

```{r}
salmon_final_graph <- ggplot(salmon, aes(x = year, y = salmon_fresh)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE, size = 0.5, color = "gray20") +
  theme_bw() +
  scale_x_continuous(expand = c(0,0), limits = c(1990, 2017)) +
  labs(x = "Year", y = "U.S. Annual Fresh Salmon Imports\n(1,000 Pounds)")

salmon_final_graph
```

